%
% Daftar Pustaka 
% 

% 
% Tambahkan pustaka yang digunakan setelah perintah berikut. 
% 
\begin{thebibliography}{4}
\bibitem{can_deep_learning} Nicholas D. LanePetko Georgiev. Can Deep Learning Revolutionize Mobile Sensing?.

\bibitem{deepear} Nicholas D. Lane, Petko Georgiev, Lorena Qendro. DeepEar: Robust Smartphone Audio Sensing in Unconstrained Acoustic Environments using Deep Learning.

\bibitem{early_Resource} Nicholas D. Lane, Sourav Bhattacharya, Petko Georgiev, Claudio Forlivesi, Fahim Kawsar. An Early Resource Characterization of Deep Learning on Wearables, Smartphones and Internet-of-Things Devices.

\bibitem{deepx} Nicholas D. Lane, Sourav Bhattacharya, Petko Georgiev, Claudio Forlivesi, Lei Jiao, Lorena Qendro, and Fahim Kawsar. DeepX: A Software Accelerator for Low-Power Deep Learning Inference on Mobile Devices.

\bibitem{smart_to_deep} Sourav Bhattacharya and Nicholas D. Lane. From Smart to Deep: Robust Activity Recognition on Smartwatches using Deep Learning. The Second IEEE International Workshop on Sensing Systems and Applications Using Wrist Worn Smart Devices, 2016

\bibitem{fast_rcnn} Ross Girshick. Fast R-CNN. 2015 IEEE International Conference on Computer Vision

\bibitem{face_occlusion} Yizhang Xia, Bailing Zhang, Frans Coenen. Face Occlusion Detection Based on Multi-task Convolution Neural Network. 2015 12th International Conference on Fuzzy Systems and Knowledge Discovery (FSKD)

\bibitem{har_mocap_fnn} Earnest Paul Ijjina, C Krishna Mohan. Human Action Recognition based on Motion Capture Information using Fuzzy Convolution Neural Networks. 

\bibitem{hand_gesture} Hsien-I Lin†, Ming-Hsiang Hsu, and Wei-Kai Chen. Human Hand Gesture Recognition Using a Convolution Neural Network. 2014 IEEE International Conference on Automation Science and Engineering (CASE) Taipei, Taiwan, August 18-22, 2014

\bibitem{fdv_hsv_batik} Nanik Suciati, Agri Kridanto, Mohammad Farid Naufal, Muhammad Machmud \& Ardian Yusuf Wicaksono. Fast Discrete Curvelet Transform And HSV Color Features For Batik Image Classification. 2015 International Conference on Information, Communication Technology and System (ICTS)

\bibitem{cnn_restoration} Xinyan Yu1, Guohao Lyu, Siwei Luo, Junbo Liu. A Convolution Neural Network Based Variational Restoration Model

\bibitem{meta_cnn} L. M. Rasdi Rere, Mohamad Ivan Fanany, Aniati Murni Arymurthy. Metaheuristic Algorithms for Convolution Neural Network. Hindawi Publishing Corporation Computational Intelligence and Neuroscience

\bibitem{cnn_transfer_learning} yejun Tang, Liangrui Peng, Qian Xu, Yanwei Wang dan Akio Furuhata. CNN based Transfer Learning for Historical Chinese Character Recognition. 2016 12th IAPR Workshop on Document Analysis Systems

\bibitem{nlp_pipeline} Giuseppe Attardi. DeepNL: a Deep Learning NLP pipeline. Proceedings of NAACL-HLT 2015, Association for Computational Linguistics

\bibitem{thin_client_computing} Thin Client Computing. 2010. Info World Deep Dive

\bibitem{ml_in_cloud} Machine Learning in the Cloud. 2010. Info World Deep Dive

\bibitem{lenet}Ynn LeCun, Leon Bottou, Yoshua Bengio and Patrick Haffner.Gradient-Based Learning Applied to Document Recognition. PROCEEDINGS OF THE IEEE, VOL. 86, NO. 11, NOVEMBER 1998.

\end{thebibliography}

